\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=0.4in, bottom=1in}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{helvet}
\usepackage{lmodern}
\usepackage{array}
\usepackage{xcolor}

\usepackage[normalem]{ulem}  % For underlining styles


\renewcommand{\familydefault}{\sfdefault} % Set the default font family to sans-serif (Helvetica)

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\definecolor{darkblue}{RGB}{0, 0, 139}
\definecolor{lightgray}{gray}{0.8}

\titleformat{\section}
  {\color{darkblue}\large\bfseries}
  {}
  {0em}
  {}
\titlespacing{\section}{0pt}{*0.8}{*0.3}

\titleformat{\subsection}
  {\color{darkblue}\normalsize\bfseries}
  {}
  {0em}
  {}
\titlespacing{\subsection}{0pt}{*0.6}{*0.2}

\titleformat{\subsubsection}
  {\color{darkblue}\normalsize\itshape}
  {}
  {0em}
  {}
\titlespacing{\subsubsection}{0pt}{*0.4}{*0.2}

\renewcommand{\labelitemi}{$\bullet$}
\setlist[itemize]{left=0pt}

\begin{document}
\setstretch{1.1}

% Header with name/title on the left and contact info on the right
\noindent
\begin{minipage}[t]{0.65\textwidth} % Left side for name and title
    {\color{darkblue}\textbf{\LARGE Saidnassimov Darkhan}} \\[0.2cm]
    \textbf{\large Software Design Engineer} \\[0.2cm]
    Self-driven software engineer with 4 years of professional experience developing and delivering software-based solutions. Interested in automation and digitization of day-to-day applications using state-of-the-art machine learning methodologies.
\end{minipage}
\hfill
\begin{minipage}[t]{0.32\textwidth} % Right side for contact information, aligned at the top
    \vspace{0pt} % Ensures proper alignment with the top of the name section
    \faPhone\ (+358) 046 550 32 34 \\[0.2cm]
    \faEnvelope\ \href{mailto:darkhan.saidnassimov@gmail.com}{\mbox{darkhan.saidnassimov@gmail.com}} \\[0.2cm]
    \faGithub\ \href{https://github.com/darkhan-s}{\mbox{github.com/darkhan-s}} \\[0.2cm]
    \faLinkedin\ \href{https://www.linkedin.com/in/dsaidnassimov/}{\mbox{linkedin.com/in/dsaidnassimov}} \\[0.2cm]
    \faMapMarker\ Helsinki, Finland
\end{minipage}

% \vspace{0.2cm}
% \hrule
% \vspace{0.1cm}

% \section*{Summary}
% Self-driven software engineer with 4 years of professional experience developing and delivering software-based solutions. Interested in automation and digitization of day-to-day applications using state-of-the-art machine learning methodologies.

\vspace{0.2cm}
\hrule
\vspace{0.1cm}

\section*{Work Experience}
\subsection*{Software Design Engineer, ABB, Helsinki, Finland \hfill \textcolor{black}{Nov 2022 - present}}
\begin{itemize}
    \item Designing the architecture of the Energy Management solution back-end.
    \item Developed anomaly detection and forecasting application plugins for the Energy Management software and maintained its core functionality.
    \item Skills: C\#.NET, RTDB (time-series database), REST API, Azure DevOps, batch scripting.
\end{itemize}

\subsection*{Thesis Worker, Metso:Outotec, Espoo, Finland \hfill \textcolor{black}{Jan 2022 - Aug 2022}}
\begin{itemize}
    \item Developed an algorithm to recognize real-life equipment items using rendered images of the corresponding 3D models, achieving mAP of 69.57\% using a custom industrial dataset.
    \item Research areas: deep learning, cross-domain object detection, transfer learning, continual learning.
\end{itemize}

\subsection*{Software Developer, Redrakon, Espoo, Finland \hfill \textcolor{black}{Oct 2021 - Jan 2022(out of business)}}
\begin{itemize}
    \item Maintained a computer vision application in a startup environment.
    \item Skills: Python, RaspberryPi, OpenVINO, Intel NCS2, OpenCV
\end{itemize}

\subsection*{Jr. Software Engineer, Raute Oyj, Lahti, Finland \hfill \textcolor{black}{July 2018 - July 2021}}
\begin{itemize}
    \item Standardized the industrial data collection system through a thesis project.
    \item Completed on and off-site installations of data collection PLC systems in 10+ plywood mills 
    \item Developed and maintained a C\# user interface for a sheet feeder, later used in 2+ customer mills.
    \item Skills: TIA, Step7, PLC, C\#.NET, Nginx
\end{itemize}

\vspace{0.2cm}
\hrule
\vspace{0.1cm}

\section*{Education}
\subsection*{Aalto University, Espoo, Finland \hfill \textcolor{black}{Sep 2020 - July 2022}}
\begin{itemize}
    \item M.Sc. in Automation and Electrical Engineering, Major in Control, Robotics and Autonomous Systems
    \item Thesis topic: Equipment identification through image recognition for Metso:Outotec (2022)
\end{itemize}

\subsection*{HAMK University of Applied Sciences, Valkeakoski, Finland \hfill \textcolor{black}{Sep 2015 - Feb 2019}}
\begin{itemize}
    \item B.Eng. in Electrical and Automation Engineering
    \item Exchange studies at the University of Dundee, Scotland, UK (2018)
    \item Thesis topic: Standardization of MillSIGHTS data collection and reporting system for Raute Oyj (2019)
\end{itemize}

\vspace{0.2cm}
\hrule
\vspace{0.1cm}

\section*{Skills: \small\textcolor{black}{\uline{Expert}, \dashuline{Intermediate}, Novice}}
\begin{itemize}
    \item \textbf{Programming:} 
      \uline{C\# (.NET)}, 
      \dashuline{Python}, 
      \uline{Matlab}
    \item \textbf{Databases:} 
      \uline{RTDB},
      \dashuline{MS SQL}, 
      \dashuline{MySQL}
    \item \textbf{DevOps \& CI/CD:} 
      \dashuline{Batch Scripting}, 
      \dashuline{GitHub Actions}, 
      Docker, 
      Kubernetes, 
      Terraform
    \item \textbf{Cloud Platforms:} 
      \dashuline{Azure DevOps}
    \item \textbf{PLC \& IoT:} 
      \uline{Step7}, 
      \uline{TIA}, 
      \uline{Raspberry Pi}, 
      \dashuline{Arduino},
      ROS
    \item \textbf{Machine Learning (Python):} 
      \dashuline{PyTorch}, 
      \uline{OpenCV}, 
      \dashuline{Pandas}, 
      \dashuline{NumPy}, 
      \dashuline{scikit-learn}, 
      \dashuline{YOLO}, 
      \dashuline{Matplotlib}
    \item \textbf{Other Skills:} 
      \uline{Linux}, 
      \uline{Git}, 
      \uline{LaTeX}, 
      \uline{JSON}, 
      \uline{XML}, 
      \dashuline{HTML/CSS},
      \dashuline{REST API},
      \uline{Microsoft Office}
    \item \textbf{Languages:} Kazakh (Native), Russian (Native), English (Fluent, IELTS 7.0), Finnish (B1, YKI-certified)
    \item \textbf{Other Certifications:} Valid Finnish Occupational Safety Card, Driving License (B)
\end{itemize}

\end{document}
